---
title: "Developing Data Products - Week3 Assignment"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

## <u><b> Objective </u></b> 
### <u><b> The objectives of this document are: </u></b> 
 - Use "quakes" dataset and create a Plot using Plotly package
 - Create an R Markdown presentation embedding the plot
 - Host the R Markdown presentation on GitHub Pages

## <u><b> Loading "quakes" Dataset </u></b> 
 - Lets load the R built in "quakes" dataset
 
```{r load_dataset}
 library(plotly)
 library(dplyr)
 data("quakes")
```

## <u><b> Adding Severities based on Magnitude </u></b> 
 - Lets assign some Severities (add a new column) as per the below guidelines. 
 - This would help later in plotting this
    * (4.0 ~ 4.9) -> low
    * (5.0 ~ 5.9) -> intermediate
    * (6.0 ~ 6.9) -> high

```{r add_color}
   quakes <- quakes %>% mutate (
     sev = case_when(
         mag >= 4.0 & mag <= 4.9 ~ "low",
         mag >= 5.0 & mag <= 5.9 ~ "intermediate",
         mag >= 6.0 & mag <= 6.9 ~ "high",
     )
   )
```

## <u><b> Scatter Plot </u></b>
```{r plot}
plot_ly(quakes, x = ~depth, y = ~mag, color = ~sev, type = "scatter")
```

## <u><b> Scatter Plot Observations </u></b>
 - There are lot of obsevations of lower magnitudes (4.0 ~ 4.9) earth quakes compared to intermediate
 - There are only 5 obvservations of higher magnitude (6.0 ~ 6.9) earth quakes
 - From the above plot, it appears that the higher magnitude (6.0 ~ 6.9) earth quakes happens at lower depths
 - Lower and Intermediate earth quakes appears to be equally distributed across all depths
